\subsection*{BENEFIT}


Solutions to the core scientific problems of the three main aims of our project will be of high impact and will lead to the future development of  software infrastructure for disaster modelling including the quantifying of uncertainty. As noted above, we anticipate being able to use other funding to add several PhD students, and other project students, to the project team and this larger team will take the entire project in the direction of building actual deliverable software. This larger team will also provide very good value to the ARC in terms of funds invested. Together with the in-kind contributions to the project, we assess in our budgeting that an ARC investment of \$x will buy \$y worth of research effort.
  As also discussed, we plan to establish contact with disaster management agencies to scope the visualisation and human interface needs of users. 

In a world that is prey to a large number of environmental risks,
the societal benefit of improved computational modelling for disaster management is huge.
This project addressess the mathematical challenges (through new approaches
to uncertainty quantification) and the software development challenges (through live coding
 for rapid prototyping) and the systems support challenges (coping with volatile and 
 rapidly changing systems environments) of one aspect (flood inundation) of this very important area.
 
In addition to the academic benefits of the research program described here, there are potential industrial benefits
through the seeding of enterprises that develop and deliver guaranteed modelling infrastructure to disaster management
agencies.

\iffalse
This research is aims to unlock the power of sophisticated
computational simulation incorporating uncertainty for
\emph{interactive} use.  Although we concentrate our research on
simulation support for disaster response, the ultimate potential of
this work is to eventually empower domain experts from a broad range
of areas to better use the high-performance computing power which is
now available to them. We envision a future where performing a complex
flood model or disaster simulation is as interactive and \emph{alive}
as flicking through photos on a tablet.\\



There are several benefits arising from the successful completion of
this project. They include, economic, societal as well as
environmental along with the generation of new knowledge:
\begin{itemize}
\item Reduced economic losses from disasters such as flooding
\item Reduced property damage from disasters
\item Reduced loss of life from disasters
\item New knowledge in the understanding of disaster modelling, and
  hence forecasting.
\end{itemize}
\fi