% list of your recent significant research outputs and ARC grants most
% relevant to this proposal (ten pages maximum).

\documentclass[a4paper,oneside,12pt]{article}
\usepackage{arcdoc}
%\setlength{\parindent}{0mm}
\renewcommand{\refname}{}

% ====================================================================

\begin{document}

\subsubsection*{F13~ Significant Publications and Research Outputs: 
PE Strazdins}

% number your research outputs continuously
% Mark with a * the research outputs most relevant to this Proposal 
% split into categories: books, book chapters, ref. journal articles,
% ref. conference papers (only if published in full)

~\\
\textbf{Scholarly Book Chapters:}
\begin{enumerate}
\item J.W. Larson, P.E. Strazdins, M. Hegland, B. Harding, S. Roberts,
  L. Stals, A.P. Rendell, Md.M. Ali, J. Southern, {\em Managing                 
    Complexity in the Parallel Sparse Grid Combination Technique}, in
  {\em Parallel Computing: Accelerating Computational Science and               
    Engineering (CSE)}, Michael Bader, Arndt Bode, Hans-Joachim
  Bungartz, Michael Gerndt, Gerhard R. Joubert, Frans Peters, eds.,
  IOS Press Ebooks, 2014, pp 593 - 602
\end{enumerate}


~\\
\textbf{Refereed Journal Articles:}

\begin{enumerate}
\setcounter{enumi}{1}
\item Muhammad Atif and Peter Strazdins,
{\em Adaptive parallel application resource remapping                           
through the live migration of virtual machines},
Future Generation Computer Systems,
37 (2014), pp 148–161

\item * M. Bernabeu, J. Southern, N. Wilson, P. Strazdins, J. Cooper and
J. Pitt-Francis, {\em                                                           
  Chaste: a case study of parallelisation of an open source                     
  finite-element solver with applications to computational cardiac              
  electrophysiology simulation,}
International Journal of High Performance Computing Applications,
IJHPCA 28(1): 13-32 (2013)

\item

  Miranda Zhang, Rajiv Ranjan, Dimitrios Georgakopoulos, Peter
  Strazdins, Samee Ullah Khan, Armin Haller, {\em Investigating Techniques      
  for Automating the Selection of Cloud Infrastructure Services}. IJNGC
  4(3) (2013)
\end{enumerate}

~\\
\textbf{Refereed Conference Papers:}
\begin{enumerate}
\setcounter{enumi}{4}
\item * Md Mohsin Ali, Peter E. Strazdins, Brendan Harding, Markus Hegland,
J. Walter Larson, {\em A Fault-Tolerant Gyrokinetic Plasma Application          
using the Sparse Grid Combination Technique}, Proceedings of the 2015
International Conference on High Performance Computing \& Simulation
(HPCS 2015), pp499-507, Amsterdam, July 2015.
{\bf (Outstanding Paper Award)}.

\item

Peter E. Strazdins, Md. Mohsin Ali, and Brendan Harding, {\em Highly            
Scalable Algorithms for the Sparse Grid Combination Technique},
Proceedings of the 2015 IEEE International Parallel \& Distributed
Processing Symposium Workshops, pp941--50, Hyderabad, May 2015.

\item

Sara S Hamouda, Josh Milthorpe, Peter E Strazdins, Vijay Saraswat, A
Resilient Framework for Iterative Linear Algebra Applications in X10,
Proceedings of the 2015 IEEE International Parallel \& Distributed
Processing Symposium Workshops, pp980--9, Hyderabad, May 2015.

\item
Md Mohsin Ali, James Southern, Peter Strazdins and Brendan Harding,
{\em Application Level Fault Recovery: Using Fault-Tolerant Open MPI            
  in a PDE Solver}, Proceedings of the 2014 IEEE International
Parallel \& Distributed Processing Symposium Workshops, pp1169-1178,
Pheonix, May 2014.

\item * Zhe Weng and Peter E Strazdins, {\em Acceleration of a
  Python-based Tsunami Modelling Application via CUDA and OpenHMPP},
  Proceedings of the 2014 IEEE International Parallel \& Distributed
  Processing Symposium Workshops, pp1275-1284, Pheonix, May 2014.

\item Chung Lee and Peter Strazdins,
  {\em An Analysis of Driver Domain Offload for Paravirtualized                 
    Communication},
Proceedings of the 12th IEEE International Conference
Trust, Security and Privacy in Computing and Communications,
TrustCom 2013; Melbourne, July 2013, pp 871-878.

\item
J.~W. Larson et al,
{\em Fault-tolerant Grid-based Solvers: Combining Concepts from                 
    Sparse Grids and MapReduce},
Proceedings of the 2013 International Conference on Computational Science,
pp 130--9, June 2013. 

\item Qian Zhang, Rajiv Ranjan, Armin Haller, Dimitrios Georgakopoulos
  and Peter Strazdins, {\em Investigating decision support techniques           
  for automating cloud service selection}, IEEE International
  Conference on Cloud Computing Technology and Science 2012,
  Taipei, Dec 2012, pp759-764.

\item Jie Cai and Peter E. Strazdins,
{\em An Accurate Prefetch Technique for                                         
Dynamic Paging Behavior for Software Distributed Shared Memory},
41st International Conference on Parallel Processing (ICPP),
pp.209-218, Sep 2012.

\item * Peter E. Strazdins,  Jie Cai, Muhammad Atif, and Joseph Antony,
{\em Scientific Application Performance on HPC, Private                         
and Public Cloud Resources: A Case Study Using                                  
Climate, Cardiac Model Codes and the NPB                                        
Benchmark Suite},
Proceedings of the 2012 IEEE International Parallel \& Distributed
Processing Symposium Workshops, pp1410-1418, Shanghai, May 2012


\item  Peter E Strazdins,
{\em Experiences in Teaching a Specialty Multicore Computing Course},
    Proceedings of the 2012 IEEE International Parallel \& Distributed
  Processing Symposium Workshops, pp1271-1276, Shanghai, May 2012

\item Jaison Mulerikkal, Peter Strazdins and Boby Thekkanath, {\em High         
Performance Cloud Computing Using an Efficient Data Service},
IEEE Asia Pacific Cloud Computing Congress 2012, Shenzen,
Nov 2012, pp 82-85.

\item * Peter Strazdins and Markus Hegland, {\em Performance Analysis
  of a Cardiac Simulation Code Using IPM}, ScalA '11: Proceedings of
  the second workshop on Scalable Algorithms for Large-scale Systems,
  pages 29--32, Supercomputing '11, ACM, Nov 2011

\item Muhammad Atif and Peter Strazdins, {\em Adaptive resource                 
  remapping through live migration of virtual machines}, in
 {\em Algorithms and Architectures for Parallel Processing},
 Lecture Notes in Computer Science, Vol 7016, pp129--143,
 Springer, Oct 2011

\item

  * Peter E. Strazdins, Margaret Kahn, Joerg Henrichs, Tim Pugh and Mike
  Rezny, {\em Profiling Methodology and Performance Tuning of the Met           
    Office Unified Model for Weather and Climate Simulations},
  Proceedings of the 2011 IEEE International Parallel \& Distributed
  Processing Symposium Workshops, pp1317-1326, Anchorage, May 2011.


\item Jaison Paul Mulerikkal and Peter Strazdins,
{\em Efficient Data Service Design for a SOA Approach to Scientific Computing},
Proceedings of the Tenth IASTED International Conference on
Parallel and Distributed Computing and Networks (PDCN 2011)
Innsbruck, Feb 2011, pp46-53.


\item * Rui Yang, Joseph Antony, Alistair Rendell, Danny Robson and Peter Strazdins,
{\em Profiling Directed NUMA Optimization on Linux Systems: A Case              
Study of the Gaussian Computational Chemistry Code},
Proceedings of the
2011 IEEE International Parallel \& Distributed Processing Symposium,
Anchorage, p1033-1042, May 2011.

\item Jaison Paul Mulerikkal and Peter Strazdins, {\em An SOA Approach
to High Performance Scientific Computing: Early Experiences},
Proceedings of the 2010  International Conference on High Performance
Computing (HiPC'10), pp 1-10, IEEE, Goa, Dec 2010.

\item Jie Cai, Peter E. Strazdins, and Alistair P. Rendell, {\em
Region-Based Prefetch Techniques for Software Distributed Shared Memory
Systems}, Proceedings of the  2010 10th IEEE/ACM International
Conference on Cluster, Cloud and Grid Computing, pages 113-122, IEEE,
Melbourne, May 2010.

\item Muhammad Atif and Peter Strazdins, {\em Optimizing Live  
Migration of Virtual Machines in SMP Clusters for HPC Applications},
Proceedings of the 6th IFIP International Conference on Network and
Parallel Computing (NPC 2009), pages 51--58, IEEE, Gold Coast, October 2009.

\item Jie Cai, Alistair P. Rendell, Peter E. Strazdins, {\em
Non-threaded and Threaded Approaches to MultiRail Communication with
uDAPL}, Proceedings of the 6th IFIP International Conference on Network
and Parallel Computing (NPC 2009), pages 233--239, IEEE, Gold Coast,
October 2008.

\item Muhammad Atif and Peter Strazdins, {\em An Evaluation of Multiple
Communication Interfaces for Virtualized SMP Clusters}, Proceedings of
the 3rd ACM Workshop on System-level Virtualization for High Performance
Computing, European Conference on Computer Systems, pp 9-16, Nuremberg,
Apr 2009.

\item * Daniel Robson and Peter Strazdins, {\em Parallelisation of the
Valgrind Dynamic Binary Instrumentation Framework}, Proceedings of   
the 2008 IEEE International Symposium of Parallel and Distributed
Processing with Applications, pages 113-121, Sydney, Dec 2008.

\item  
* Jie Cai, Alistair Rendell, {Peter Strazdins} and Hsien Jin Wong, {\em
  Performance Models for Cluster-Enabled OpenMP Implementations},
Proceedings of The Thirteenth IEEE Asia-Pacific Computer Systems
Architecture Conference (ACSAC 2008), August 2008.

\item Hsien Jin Wong, Jie Cai, Alistair Rendell and {Peter Strazdins}, 
 {\em Micro-benchmarks for Cluster OpenMP Implementations:
      Memory Consistency Costs} 
      In R.\ Eigenmann and B.R.\ de Supinski (Eds.): IWOMP 2008, LNCS
      5004, pp.\ 60--70, 2008. Springer-Verlag Berlin, April, 2008.

\item {Peter Strazdins}, {\em Applying the Community of Practice Approach to Individual
      IT Projects},
      Proceedings of the Tenth Australasian Computing Education
      Conference (ACE 2008), Wollongong, NSW, Australia. Published in
      \emph{Conferences in Research and Practice in Information
      Technology} (CRPIT), vol.\ 78, pp.\ 137--146, January 2008.

\item  * Andrew Over, Bill Clarke and Peter Strazdins,
{\em A Comparison of Two Approaches to Parallel Simulation of
      Multiprocessors},
      IEEE International Symposium on Performance Analysis of
      Systems and Software (ISPASS'07), San Jose, April 2007.

\item * {Peter Strazdins}, Bill Clarke and Andrew Over,
	{\em Efficient Cycle-Accurate Simulation of the UltraSPARC III
      CPU}, 
      Thirtieth Australasian Computer Science Conference (ACSC2007),
      pp.\ 221--228, Ballarat, Australia, January 2007.

\item {Peter Strazdins}, Richard Alexander and David Barr, 
{\em Performance Enhancement of SMP Clusters with Multiple
      Network Interfaces Using Virtualization},
            In Frontier on High Performance Computing and Networking,
      Lecture Notes in Computer Science (LNCS), vol.\ 4331, pp.\
      452--463, Springer-Verlag, 2006.

\item * Andrew Over, {Peter Strazdins} and Bill Clarke,
{\em Cycle Accurate Memory Modelling: A Case-Study in Validation},
Proceedings of the IEEE International Symposium on Modeling,
      Analysis, and Simulation (MASCOTS'05), pp.\ 85--94, Atlanta,
      September 2005.

\end{enumerate}

\newpage

\textbf{G11~ ARC Grants awarded over the last 10 years -- PE Strazdins}

\begin{center}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\bf Project Id & \bf CI/PI Names & \bf Amount & \bf Years & \bf Project Title & 
\bf Research \\
		&	&     & \bf Funded &	& Outputs	 
\\
\hline
LE150100030 & V Sivaraman & \$270,000 & 1 (2011-) 
			   & Test-bed for Wide-Area Software & \\
	 & et al &&& Defined Networking Research  & \\
\hline

LP110200410 & T Hegland, & \$446,000 & 3 (2011-) 
			   & Robust numerical solution of & 1, 3, 5, 6,\\
	 & PE Strazdins, &&& partial differential equations on  & 8, 9, 11, \\
	 & S Roberts, &&& petascale computer systems with  &  17 \\
	 & RP Brent, 	 &&& applications to tsunami modelling & \\
         & AP Rendell &&& and plasma physics &\\
         & R Nobes &&&& \\

\hline

LP100200079 & PJ Christen, & \$253,341 & 3 (2010-) 
			   & Exposing the anonymous attacker: & \\
	 & PE Strazdins, &&& Detecting identity crimes using & \\
	 & RW Gayler 	 &&& real-time entity resolution on  &  \\
& 	 &&& large dynamic databases & \\
\hline

LP0774896 & AP Rendell, & \$240,000 & 3  (2007-) 
			    & Programming Paradigms, Tools  &  21, \\
	  & PE Strazdins, &&& and Algorithms for Electronic & 27 \\
	  & MJ Frisch,     &&&  Calculations on Clusters of  & \\
	  &  GW Trucks, &&& Non-Uniform Memory Parallel & \\
	  & S See &&& Processors & \\
\hline
LP0669762 & PE Strazdins, & \$147900 & 3 (2006-) 
			    & Accurate Performance Modelling & 16, 20, \\
	  & PD Coddington &&& and Prediction of Cluster & 22 \\
	  &		  &&& Computers & \\
\hline 
LP0669726 & AP Rendell,  & \$250,000 & 3 (2006-) 
			    & Next Generation Grid Enabled  & 13, 23, \\
	  & PE Strazdins &&& Cluster Computers: Performance & 25, 28, \\
	  &		 &&& Optimisation for e-Research & 29\\
\hline
\end{tabular}
\end{center}		



\end{document}
