\documentclass[a4paper,oneside,12pt]{article}
\usepackage{arcdoc}

%

%\usepackage[square, comma, sort&compress]{natbib}

\pagestyle{empty}

%\setlength{\parindent}{0mm}
\renewcommand{\refname}{}

% ====================================================================

\begin{document}

\subsubsection*{H2 Progress Report for LP100200079}

\begin{tabbing}
\textbf{Funding Scheme:} \= bla bla \kill
%\textbf{Project ID:} \> LP100200079 \\
\textbf{Project Title:} \> Exposing the anonymous attacker: Detecting
  identity crimes using real-time entity resolution \\
~ \> on large dynamic databases \\
\textbf{Project Leader:} \> A/Prof Peter Christen \\
\textbf{Funding Scheme:} \> Linkage Project
\end{tabbing}

\noindent
{\bf Project Summary:} \\
With the widespread use of electronic transactions it has become
essential to verify the identity of absent participants with a high
level of certainty. Due to the difficulty of electronic identity
verification, identity crimes are on the increase. They can result in
losses of billions of dollars to financial organisations and grave
implications for the victims concerned. The aim of this project is to
develop a new generation of real-time entity resolution techniques
that will significantly improve electronic identity verification. The
outcomes will be novel parallel indexing and classification techniques
for entity resolution that are scalable to large databases, work on
dynamic databases, and can incorporate user constraints. \\[-2mm]

\noindent
{\bf Current Status:~} \\
This project has started in February 2012. This delay (which
is approved by the ARC) was primary because the negotiations of the
partner agreement with the two industry partners (Veda and Funnelback,
Pty.\ Ltd.) were more time consuming than expected, due to Commonwealth
privacy legislation requiring elaborate
access and confidentiality arrangements. As a result of this the
transfer of the real data to the ANU was delayed until June
2013. Further issues arose in late 2013 when one of the partner
investigators left his organisation, leading to the withdrawal of
partner organisation Funnelback in 2014.

Despite these issues, we have achieved many of the project goals so
far, and we continue to work on improved automatic real-time
matching. One exception was in parallel entity resolution, where no
satisfactory results could be obtained due to unexpected limitations in current
Python interpreters (our code infrastructure is purely Python-based).
  The PhD student has submitted her PhD thesis in late
October 2015, and we anticipate to complete the project by the end
of 2015. \\[-2mm]

\noindent
The following major publications (ordered chronologically) have been
produced.
%
\setlength{\leftmargini}{5mm}
\begin{enumerate}
%\setlength{\itemsep}{0.5ex plus0.1ex}
\setlength{\itemsep}{0mm}
\item {\em Efficient Entity Resolution with Adaptive and
      Interactive Training Data Selection}. \\
      Qing Wang, Dinusha Vatsalan and Peter Christen. IEEE ICDM,
      Atlantic City, November 2015.
\item {\em Context-aware Approximate String Matching for Large-scale
      Real-time Entity Resolution}. \\
      Peter Christen and Ross Gayler. DINA workshop held at IEEE ICDM,
      Atlantic City, November 2015.
\item {\em Dynamic Sorted Neighborhood Indexing for Real-Time
      Entity Resolution}. \\
      Banda Ramadan, Peter Christen, Huizhi Liang, and Ross Gayler.
      ACM JDIQ, 2015.
\item {\em Efficient Interactive Training Selection for Large-scale
      Entity Resolution}. \\
      \textbf{Qing Wang}, \textbf{Dinusha Vatsalan} and \textbf{Peter
      Christen}; PAKDD'15; Ho Chi Minh City, Vietnam, May 2015.
\item {\em Unsupervised Blocking Key Selection for Real-Time Entity
      Resolution}. \\
      Banda Ramadan and \textbf{Peter Christen}; PAKDD'15; Ho Chi Minh
      City, Vietnam, May 2015.
\item {\em Real-time Collaborative Filtering Recommender Systems.} \\
      Huizhi Liang, Haoran Du and \textbf{Qing Wang}; AusDM'14,
      Brisbane, November 2014.
%      Proc.\ of the 12th Australasian Data Mining Conference
%      (AusDM'14), Brisbane,  CRPIT, November 2014. 
%\item {\em Forest-Based Dynamic Sorted Neighborhood Indexing for
%      Real-Time Entity Resolution.} \\
%      Banda Ramadan and \textbf{Peter Christen}; poster paper;
%      CIKM'14, Shanghai, November 2014.
%      Poster paper.
%      Proc.\ ACM International Conference on Information
%      and Knowledge Management (CIKM'14), Shanghai, November 2014.
\item {\em Dynamic Sorted Neighborhood Indexing for Real-Time Entity
      Resolution.} \\
      Banda Ramadan, \textbf{Peter Christen} and Huizhi Liang; ADC'14;
      Brisbane, July 2014.
%      Proc.\ Australasian Database Conference (ADC'14),
%      Brisbane, July 2014.
\item {\em Noise-Tolerant Approximate Blocking for Dynamic
      Real-time Entity Resolution.} \\
      Huizhi Liang, Yanzhe Wang, \textbf{Peter Christen}, and
      Ross Gayler; PAKDD'14, Tainan, Taiwan, May 2014.
%      Proc.\ Pacific-Asia Conference on Knowledge
%      Discovery and Data Mining (PAKDD'14), Tainan, Taiwan, May 2014.

\item {\em Two Stage Similarity-aware Indexing for Large-scale
      Real-time Entity Resolution.} \\
      Shouheng Li, Huizhi Liang and Banda Ramadan; AusDM'13,
      Canberra, November 2013.
%      Proc.\ of the 11th Australasian Data Mining Conference
%      (AusDM'13), Canberra, CRPIT, November 2013.
%\item {\em Flexible and Extensible Generation and Corruption
%      of Personal Data.} \\
%      \textbf{Peter Christen} and \textbf{Dinusha Vatsalan};
%     poster paper; CIKM'13, San Francisco, October 2013.
%      Poster paper.
%      Proc.\ of the ACM International Conference on
%      Information and Knowledge Management (CIKM 2013), San
%      Francisco, October 2013.
\item {\em Adaptive Temporal Entity Resolution on Dynamic
      Databases.} \\
      \textbf{Peter Christen} and Ross Gayler; PAKDD'13,
      Gold Coast, Australia, April 2013.
%      Proc.\ of the Pacific-Asia Conference on Knowledge
%      Discovery and Data Mining (PAKDD'13), Gold Coast,
%      Australia, April 2013.
\item {\em Dynamic Similarity-Aware Inverted Indexing for Real-Time
      Entity Resolution.} \\
      Banda Ramadan, \textbf{Peter Christen}, Huizhi Liang,
      David Hawking, and Ross Gayler; DMApps workshop held at
      PAKDD'13, Gold Coast, Australia, April 2013.
%      Proc.\ of the International Workshop on Data Mining
%      Applications in Industry and Government (DMApps), held at
%      PAKDD'13, Gold Coast, Australia, April 2013.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
