\iffalse
\subsection*{ROLE OF PERSONNEL}
\fi
\subsection*{INVESTIGATORS}

% - Summarise the role, responsibilities and contributions of each Chief Investigator (CI) and Partner Investigator (PI)
% - Summarise the roles and levels of involvement of other Participants, for example, technical staff, Research Associates and other personnel
% - Describe how each Participant will ensure they have the ‘time and capacity’ to undertake the proposed research, taking into account any other grants or roles that they hold.

%The personnel on this grant cover the key research areas discussed in
%the \emph{Research Project} section of this application:
%
%\begin{itemize}
%\item \textbf{Steve Roberts}: uncertainty quantification, sparse grids, flood
%  modelling
%\item \textbf{Markus Hegland}: sparse grids
%\item \textbf{Peter Strazdins}: sparse grids, distributed computing
%\item \textbf{Henry Gardner}: HCI, interfaces
%\end{itemize}


The personnel involved in this project will be CIs Gardner, Strazdins,
Roberts and Hegland, two Post-doctoral Research Associates and five
PhD students. This project is split equally between the ANU Research
School of Computer Science and the ANU Mathematical Sciences
Institute. The four CIs are senior academics with many years of
experience in running projects and many years of experience working
with each other. Even though CI Gardner is the lead CI on this 
application, the management structure of the project will be flat and
deeply collaborative.


{\bf CI Gardner} will be responsible for the overall project and for leading Aim 2. He is a senior
academic with many years of experience in computational science, high
performance computing, virtual reality, Human Computer Interaction and
computer music. He was director and head of school of ANU Computer
Science from 2008 to 2013 and is presently the Associate Dean of
Higher Degree Research in the ANU College of Engineering and Computer
Science. In recent years, CI Gardner has been leading a research group
that has developed the live coding ``Extempore'' programming
system. This system originated in the creative arts to support live
computer music and it has recently been shown to effectively harness and
``enliven'' HPC computational science applications in
real time with negligible performance overhead. CI Gardner has a 40\%
research allocation and his term as Associate Dean will expire before 2018, and
he has no other grant commitments at the present time, 
providing him with opportunity to provide the proposed 20\% allocation
to the present project. 
%
{\bf CI Strazdins} will be responsible for the high performance and
distributed computing components of the project (Aim 3), based on his
expertise in high performance computing, where he has a number of
significant and well cited publications
~\parencite{AliEtal2015,sgctalg15,Ali11022016}.  CI Strazdins
has a 40\% research allocation and has no present grant commitments in 2018, leaving sufficient research time to
cover the proposed 20\% allocation to this project.
%
{\bf CI Roberts} will lead the inundation simulation model development and will 
collaborate with CI Hegland to provide leadership of the 
uncertainty quantification part of the project (Aim 1). CI Roberts has extensive 
expertise in computational
fluid dynamics and uncertainty
quantification~\parencite{deBaarRDM2015,JakemanRoberts2013,anugamanual,nielsen2005hydrodynamic}.
CI Roberts has a 40\% research allocation, with no current grant
obligations, leaving sufficient research time to cover the proposed
20\% allocation to this project.
%
As mentioned, {\bf CI Hegland} will collaborate with CI Roberts in the leadership of the mathematical aspects of
this project. He will also lead the reduced-basis aspects of uncertainty quantification. CI Hegland has extensive expertise in
computational mathematics and is well-known for his expertise in the analysis
of the combination technique for sparse
grids~\parencite{AliEtal2015,HardingHLS2015,Ali11022016}.  CI Hegland
has a 60\% research allocation. In 2018 will he contribute 20\% of his
research time to the DP150102345, and potentially a 20\% contribution
to LP160100624 leaving sufficient research time to cover the proposed
20\% allocation to this project.


Our project is strengthened by a collaboration  with Dr
Bert Debusschere and Dr John Jakeman both from Sandia National
Laboratories, USA. Dr Debusschere
has extensive expertise in uncertainty quantification and fault
tolerant numerical solvers and has already collaborated with CI
Strazdins~\parencite{parSGCT16}.  
Dr Jakeman has expertise on uncertainty
quantification techniques based on his extensive experience in using
adaptive sparse grids, having applied such techniques to complex
modelling problems~\parencite{JakemanRoberts2013,jakemanNumerical2010,
  Jakeman2015} and has already collaborated with CI Roberts (his
former PhD supervisor)~\parencite{JakemanRoberts2013}.  

\iffalse
Both  Dr Debusschere and Dr Jakeman
have offered to host visits from our group to the Livermore and
Albuquerque Sandia Laboratories. We plan to support reciprocal visits
to ANU.
\fi

{\bf One post-doctoral fellow} will be situated in the Research School
of Computer Science (RSCS) and will develop large portions of the live
programming tools and software interface which will interact with the
scientific models and will conduct experiments on live scenarios where
human actors mimic the interactions and information flows involved in
the group dynamics of disaster response with simulation support. Due
to the large skill set and responsibilities of this position it has
been factored into the budget at level B3.  One possible candidate for
this position is Dr Ben Swift who is currently a post doc in the RSCS, a
former PhD student of CI Gardner, and someone who has
deep expertise relevant to this project
~\parencite{martin2015tracking,martin2016intelligent,swiftLive2016,
  swift2013visual,swift2014coding}. Another possible candidate is Mr 
  Andrew Sorensen who is a software developer, a published researcher, and a
   world recognised live-coding exponent of many years experience. 
  Mr Sorensen is about to complete his PhD, studying with CI Gardner, based
  on his work with the Extempore system of which he is the lead author.

{\bf A second post-doctoral fellow} will be situated in the
Mathematical Sciences Institute (MSI) and will develop the numerical methods for computing
sparse grid surrogates and reduced basis models which will be used to
efficiently propagate uncertainties in model applications of tsunami
and flood surge events. This position is budgeted at level B2.  One possible candidate for this position Dr Brendan Harding, who 
is the former PhD student of CI Hegland and who has
collaborated with CIs Hegland, Strazdins and Roberts on work
relevant to this project~\parencite{Ali11022016, AliEtal2015,
  deBaarHarding2015, HardingHLS2015, sgctalg15}.


We are requesting ARC funding for {\bf two PhD students}, and we anticipate
obtaining funding for {\bf another three PhD students} from Australian Postgraduate
Awards. Even though we have designated these PhD students to be for 
specific projects in computer science or mathematics, all of their projects will be
interdisciplinary, with all four CIs being on the supervisory panels
of each of the students. 

\iffalse
. In RSCS, these will be the dynamic distributed
computing infrastructure and the development of live interfaces for
data visualisation. In the MSI, these will be the uncertainty
quantification and the development of numerical methods for the sparse
grid technique, and the reduced basis method, applied to our
inundation model example. 
\fi

\iffalse
We anticipate being able to support several
Honours projects in computer science and mathematics during this
project.  Some of these projects will relate to the core mission of
the project detailed above, while others will concentrate on related
studies with a view to achieving high-impact pure and applied research
and training young people for a career in the computing and
mathematical modelling disciplines
\fi

\iffalse
We anticipate being able to support a number of Honours projects in
computer science and mathematics during the course of this
project. Some of these projects will relate to the core mission of the
project detailed above, others will concentrate on related studies
with a view to achieving high-impact pure and applied research and
training young people for a career in the computing and mathematical
modelling disciplines.
\fi

