\subsubsection*{Other projects}

The two postdoctoral fellows and three of the five PhD students 
will be concerned with the main aims of this grant application: One postdoctoral fellow and one PhD student in 
Mathematics will study storm surge equations in realistic topographies with the calculation of uncertainty. They will work closely with the other postdoctoral fellow 
and one PhD student in Computer Science to study the application of live coding to uncertainty quantification of these equations. The third
PhD student will work with the postdoctoral fellow in Computer Science to study  live coding of the HPC infrastructure for these systems.

The remaining two PhD students will study other aspects of the overall context shown in Figure 1. One PhD student in Mathematics will study other environmental models of relevance
to disaster management such as ..... The other PhD student will study the human-computer-interaction context of real-time disaster management. 
Similar to the impact of visually presented geodata on decision
making~\parencite{kinkeldey2015evaluating}, the particular
visualisations of uncertainty in our environmental models will need to
be systematically evaluated with human participants. Here we will
adopt traditional human-factors trials with non-expert participants
together with qualitative feedback from emergency services experts. We
will solicit qualitative feedback from expert participants from
emergency authorities in our local area including ACT Emergency
Services, Geosciences Australia, the Australian Maritime and Safety
Authority and the Australian Federal Police. Perspectives offered by
this participant pool will be important in extrapolating our study
results to real world disaster-management.

We also anticipate a number of Honours and other student projects concerned with the overall context of our research.



 



